Evolution Reinforces Cooperation with the Emergence of Self-Recognition Mechanisms: an Empirical Study of the Moran process for the Iterated Prisoner's Dilemma

### 2017-10-30 main.tex
Add p values of a t test.

Comparisons of \(x_1, x_{N/2}, x_{N-1}\) are shown in
Figure~\ref{fig:comparison_deterministic}. 
The top most line on all figures (in red and using a circle) corresponds to
\(x_{N-1}\), the middle line (in green and using a cross) corresponds to
\(x_{N/2}\) and the bottom line (in blue and using an x) corresponds to
\(X_{1}\).
The points represent the simulated
values and the line shows the theoretical value. Note that these are all
deterministic strategies and show a perfect match between the expected value
of (\ref{equ:fixation_probability}) and the actual Moran process for all
strategy pairs. Figure~\ref{fig:comparison_stochastic} shows the fixation probabilities for
stochastic strategies. These are no longer a good match which highlights the
% TODO Rephrase this sentence: possibly when doing the statistical test
weakness of assuming a given interaction between two IPD strategies can be
summarised with a set of utilities as shown in
(\ref{equ:payoff_matrix}). For any given pair of strategies it is possible to
obtain \(p_{i,i-1}, p_{i,i+1}, p_{ii}\) exactly (as opposed to the
approximations offered by (\ref{equ:p_up}), (\ref{equ:p_down}) and
(\ref{equ:p_stay})). Obtaining these requires particular analysis for a given
pair and can be quite a complex endeavour for stochastic strategies with long
memory: this is not necessary for the purposes of this work.
All data generated for this validation exercise can be found
at \cite{data}.
% TODO Include a statistical test (1 sided t test)

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.5\columnwidth}
        \centering
        \includegraphics[width=.95\columnwidth]{img/Alternator_v_Cooperator.pdf}
        \caption{Alternator and Cooperator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.5\columnwidth}
        \centering
        \includegraphics[width=.95\columnwidth]{img/Alternator_v_TfT.pdf}
        \caption{Alternator and Tit For Tat}
    \end{subfigure}%

    \begin{subfigure}[t]{.5\columnwidth}
        \centering
        \includegraphics[width=.95\columnwidth]{img/WSLS_v_TfT.pdf}
        \caption{Win Stay Lose Shift and Tit For Tat}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.5\columnwidth}
        \centering
        \includegraphics[width=.95\columnwidth]{img/Alternator_v_WSLS.pdf}
        \caption{Alternator and Win Stay Lose Shift}
    \end{subfigure}%
    \caption{Comparison of theoretic and actual Moran Process fixation
             probabilities for \textbf{deterministic} strategies.}
    \label{fig:comparison_deterministic}
\end{figure}

\begin{figure}[!hbtp]
    \centering

    \begin{subfigure}[t]{.5\columnwidth}
        \centering
        \includegraphics[width=.95\columnwidth]{img/ALLCorALLD_v_Cooperator.pdf}
        \caption{All C or all D and Cooperator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.5\columnwidth}
        \centering
        \includegraphics[width=.95\columnwidth]{img/Calculator_v_ALLCorALLD.pdf}
        \caption{Calculator and All C or all D}
    \end{subfigure}%

    \begin{subfigure}[t]{.5\columnwidth}
        \centering
        \includegraphics[width=.95\columnwidth]{img/Calculator_v_Arrogant_QLearner.pdf}
        \caption{Calculator and Arrogant Q learner}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.5\columnwidth}
        \centering
        \includegraphics[width=.95\columnwidth]{img/ALLCorALLD_v_TfT.pdf}
        \caption{All C or all D and Tit For Tat}
    \end{subfigure}%
    \caption{Comparison of theoretic and actual Moran Process
             fixation probabilities for \textbf{stochastic} strategies.}
    \label{fig:comparison_stochastic}
\end{figure}

>>>>

Comparisons of \(x_1, x_{N/2}, x_{N-1}\) are shown in
Figure~\ref{fig:comparison_deterministic} for Alternator and WSLS.
The top most line on all figures (in red and using a circle) corresponds to
\(x_{N-1}\), the middle line (in green and using a cross) corresponds to
\(x_{N/2}\) and the bottom line (in blue and using an x) corresponds to
\(X_{1}\).
The points represent the simulated
values and the line shows the theoretical value. Note that these are 
deterministic strategies and show a good match between the expected value
of (\ref{equ:fixation_probability}) and the actual Moran process for all
strategy pairs. These means have been compared using a \(t\)-test and the \(p\)
values are shown in Table~\ref{tab:comparison_deterministic} which confirms the
fact that the theoretic and simulated values are a good match.

Figure~\ref{fig:comparison_stochastic} shows the fixation probabilities for
stochastic strategies: Calculator and arrogant Q Learner. These are no longer a
good match (confirmed with a \(t\)-test in
Table~\ref{tab:comparison_stochastic}) which highlights the weakness of assuming
a given interaction between two IPD strategies can be summarised with a set of
utilities as shown in (\ref{equ:payoff_matrix}). For any given pair of
strategies it is possible to obtain \(p_{i,i-1}, p_{i,i+1}, p_{ii}\) exactly (as
opposed to the approximations offered by (\ref{equ:p_up}), (\ref{equ:p_down})
and (\ref{equ:p_stay})). Obtaining these requires particular analysis for a
given pair and can be quite a complex endeavour for stochastic strategies with
long memory: this is not necessary for the purposes of this work.  All data
generated for this validation exercise can be found at~\cite{data}.

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.95\columnwidth]{img/Alternator_v_WSLS.pdf}
    \caption{Comparison of theoretic and actual Moran Process fixation
             probabilities for \textbf{deterministic} strategies: Alternator and
             Cooperator.}
    \label{fig:comparison_deterministic}
\end{figure}

\begin{table}[!hbtp]
    \centering
    \input{tex/t_test_results_alternator_v_wsls.tex}
    \caption{\(p\) values resulting from a $t$ test comparing the theoretic
        value with the simulated value of the Moran Process fixation
        probabilities for \textbf{deterministic} strategies: Alternator and
    Cooperator.}
    \label{tab:comparison_deterministic}
\end{table}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.95\columnwidth]{img/Calculator_v_Arrogant_QLearner.pdf}
    \caption{Comparison of theoretic and actual Moran Process
             fixation probabilities for \textbf{stochastic} strategies:
             Calculator and Arrogant Q Learner.}
    \label{fig:comparison_stochastic}
\end{figure}

\begin{table}[!hbtp]
    \centering
    \input{tex/t_test_results_calculator_v_arrogant_q_learner.tex}
    \caption{\(p\) values resulting from a \(t\) test comparing the theoretic
        value with the simulated value of the Moran Process fixation
        probabilities for \textbf{stochastic} strategies: Calculator and
    Arrogant Q Learner.}
    \label{tab:comparison_stochastic}
\end{table}
